---
title: "I have the best titles"
author: Your name here
subtitle: Subtitle here if desired
---

# Introduction
My really awesome and complete introduction will go here.  

> I know words.  I have the best words.  ~ Donald Trump

# Materials and methods

Narrative and most code will go here.  Describe what you are doing and show how to do it (with code).

You can do bullets like this:

* The first most important thing
* The second most important thing
* The third most important thing

You can do numbers like this:

1. The first most important thing
2. The second most important thing
3. The third most important thing

See [http://rmarkdown.rstudio.com/](http://rmarkdown.rstudio.com/) for all the amazing things you can do.


Here's my first code chunk.
```{r}
1+2
```

Load any required packages in a code chunk (you may need to install some packages):

```{r, message=F, warning=F}
library(dplyr)
library(ggplot2)
library(maps)
#library(spocc)
knitr::opts_chunk$set(cache=TRUE)  # cache the results for quick compiling
```




```{r, warning=F} 





# Results


```

```{r}

```

# Conclusions

What have you learned?  Are there any broader implications?

# References

